We have set up Dionaea on our AWS server and it is successfully collecting logs. Some further configuration may be required in order to ensure that we are logging at an appropriate level. We also plan to install and configure more modules for Dionaea including some for logging and some for adding more vulnerabilities. We also have Cowrie running on our AWS server. Modern Honeypot Network is running and provides up to date data collected by Dionaea and Cowrie, which already provides some high level insights. We may add additional sensors to MHN later on. 

We have also configured the AWS server's firewall and security groups. Currently we are allowing all inbound network traffic on all ports and denying all outbound traffic. SSH access is restricted to our own SSH keys. Password logins are denied and root login is also denied. So far we have logged numerous attempts from scanners to log on to our service, and Dionaea has already captured a few malware binaries. 

For data analysis, we used the mongoexport command line tool to export data collected by MHN to JSON files. We would secure copy these files onto our local machines and use jupyter notebooks to explore data. Primarily, the matplotlib, numpy, and pandas libraries were used to aid the development of our findings. Additionally, we modified MHN to include a new webpage for particularly interesting findings. Such findings were generated from a daily cron job we set up on the server to run scripts that we developed locally.